Predicting Music Emotion: Insights from Canadian Weather and Spotify Audio Features

### 2024-12-06 paper/paper.qmd
currently re-reading my paper- pls don't graded it yet!

```{r}
#| echo: false
#| eval: true
#| label: fig-assumptions
#| fig-cap: "Residuals vs Fitted and Normal Q-Q Plot"
#| warning: false
#| fig-align: center
#| fig.width: 5.5
#| fig.height: 3.5
# Arrange plots side by side
par(mfrow = c(1, 2))

>>>>

```{r}
#| echo: false
#| eval: true
#| label: fig-assumptions
#| fig-cap: Residuals vs Fitted and Normal Q-Q Plot
#| warning: false
#| fig-align: center
#| fig.width: 5.5
#| fig.height: 3.5
# Arrange plots side by side
par(mfrow = c(1, 2))
